Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-05-18 paper.tex
writing for the similarity section

\subsection{Modeling similarity between figures}

\begin{figure}
  \begin{minipage}{0.4\textwidth}
  \includegraphics[width = 3in]{figures/NMF.png}
  \caption{NMF on features of the programs that were synthesized for each image. Horizontal component roughly corresponds to ``symmetry'' while vertical component roughly corresponds to ``loopyness'', with images on the diagonal having both of these.}    
    \end{minipage}\hfill
\begin{minipage}{0.4\textwidth}
  \includegraphics[width = 3in]{figures/imageSimilarity.png} 
  \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
    \end{minipage}
  \end{figure}

>>>>

\subsection{Modeling similarity between drawings}
Modeling an image using a program opens up new ways of measuring similarity between drawings.
For example, we might say that two drawings are similar if they both contain repetitions of length 4,
or if they share the same reflectional symmetry,
or if they are both organized according to a grid-like structure.

We measure the similarity between two drawings by extracting features
of the best programs that describe them.  Here the features we use are
just counts of the number of times that different components in the
DSL were used (Table~\ref{DSL}).  We project these features down to a
2-dimensional subspace using nonnegative matrix factorization
(NMF:~\cite{lee1999learning}); see Fig.\ref{NMF}.  One could use many
alternative similarity metrics between drawings which would capture pixel-level or object-level similarities while missing high-level geometric similarities.
For example, we can use our learned distance metric between execution traces, $L_{\text{learned}}(\cdot|\cdot)$.
Projecting these distances to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}) reveals similarities between the objects in the drawings,
while missing similarities at the level of the program.
\begin{figure}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width = 3in]{figures/NMF.png}
    \caption{NMF on features of the programs that were synthesized for each image. Horizontal component roughly corresponds to ``symmetry'' while vertical component roughly corresponds to ``loopyness'', with images on the diagonal having both of these.}    \label{NMF}
  \end{minipage}\hfill
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width = 3in]{figures/imageSimilarity.png} 
    \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
  \end{minipage}
\end{figure}
